---
title: "Tooth growth dataset: exploratory data analysis"
author: "Maximiliano"
date: "10/11/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The dataset {.smaller}

Available in the *R datasets package*, ToothGrowth dataset compares **tooth growth** in 60 guinea pigs **by supplement type** (OJ: Orange Juice | VC: Ascorbic acid) **and dose** in milligrams/day.

*Some of the first rows*
```{r, comment=""}
head(ToothGrowth,3)
```

*Summary*
```{r, comment=""}
summary(ToothGrowth)
```

## Panel Boxplot {.smaller}
```{r, warning=FALSE, message=FALSE, fig.align='center', fig.height=4}
library(plotly)
plot1 <- plot_ly(y=ToothGrowth$len, color=factor(ToothGrowth$supp) ,type="box", boxpoints = "all") %>% layout(title = "Tooth lenght by supplement type", yaxis=list(title="Tooth Length"),xaxis=list(title="Supplement type (OJ: Orange Juice | VC: Ascorbic acid)"))
plot1
```
\
*From the panel boxplot above it is not clear if one of the supplements is better. We could do an hypothesis tests to verify this.*





